\documentclass[a4paper,12pt]{article}
\input{preart_ru}

\begin{document}

\thispagestyle{empty}
\begin{center}
    Computer Science Center

    Yandex ML \& Data Management Lab
\end{center}
\vspace{13ex}

\begin{center}
    \vspace{16ex}
    \begin{spacing}{1.5}
        {\Large Контрактное программирование \\как способ задания и оптимизации вычислительных графов для распределённых потоковых систем}
    \end{spacing}
\end{center}
\vfill
\begin{flushright}
    \noindent
    \textit{Руководитель: Трофимов Артём} \\
    \textit{Студент: Стоян Андрей}
\end{flushright}
\vspace{5ex}
\begin{center}
    СПб 2020
\end{center}
\newpage

\tableofcontents
\newpage

\input{intro.tex}
\newpage
\input{problem.tex}
\newpage
\input{idea.tex}
\newpage
\input{impl.tex}
\newpage
\input{results.tex}
\input{future-work.tex}
\input{conclusion.tex}
\input{appendix-a.tex}

\begin{thebibliography}{9}
    \bibitem{flink-org} Apache Flink: \url{https://flink.apache.org/}.
    \bibitem{streaming-sql} Реализация диалекта Streaming SQL в Apache Calcite: \url{https://calcite.apache.org/docs/stream.html}.
    \bibitem{hoare} Bornat, Richard. "Proving pointer programs in Hoare logic." International Conference on Mathematics of Program Construction. Springer, Berlin, Heidelberg, 2000.
    \bibitem{beam} Apache Beam: \url{https://beam.apache.org/}.
    \bibitem{beam-py} Apache Beam Python API: \url{https://beam.apache.org/documentation/sdks/python/}.
    \bibitem{haskell} Haskell: \url{https://www.haskell.org/}.
    \bibitem{beam-transforms} Core Beam transforms: \url{https://beam.apache.org/documentation/programming-guide/#core-beam-transforms}.
    \bibitem{liquidhaskell} Vazou, Niki, et al. "Refinement types for Haskell." Proceedings of the 19th ACM SIGPLAN international conference on Functional programming. 2014.
    \bibitem{rowpoly} Gaster, Benedict R., and Mark P. Jones. A polymorphic type system for extensible records and variants. Technical Report NOTTCS-TR-96-3, Department of Computer Science, University of Nottingham, 1996.
\end{thebibliography}

\end{document}
